A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-09-13 journal/relatedwork.tex
SCB

>>>>

One recent approach does, at a conceptual level, resemble our methods:  \emph{semantic crash bucketing} (SCB) improves the fuzzer taming ability of AFL \cite{aflfuzz}, Honggfuzz \cite{honggfuzz}, and CERT BFF \cite{BFF}, by approximating real bug fixes with lightweight program modifications \cite{SCB}.  The primary difference between SCB and our approach is that we generate many more potential approximate fixes, via mutation, but use no semantic feedback from failing inputs other than code coverage.  The selectivity of SCB dramatically improves its scalability and ease-of-use, but limits applicability to cases where a patch template has been manually constructed, e.g., buffer overruns and null pointer dereferences.  While these cases are by far the most common in traditional security/crash-based fuzzing, crashes are usually the \emph{uninteresting} cases in compiler fuzzing, or fuzzing/symbolic-execution based property-based \cite{ClaessenH00} testing \cite{DeepState,DeepStateTutorial,deepstaterepo}.  It is unlikely that enough patch templates for the interesting changes to compiler code, or invariant-preserving code in other fuzzing, can be manually produced to make SCB alone generalize to these settings.  Another difference is that SCB provides bucketing, rather than ranking; this is in some cases ideal (a user of AFL usually just wants to count ``different'' vulnerabilities that are memory-safety based), but in settings where the fixes are even more approximate and overlapping, and the bugs more complex, ranking is most useful.
